A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-11 evaluation.tex
Ostrich evaluation sketch

>>>>

\subsection{Evaluation in \Ostrich{}}\label{}%
\Catra{} was experimentally integrated as the Parikh automata product solver for
an in-progress version of \Ostrich{} (which shares \Princess{} as the backing
theorem prover) with cost-enriched automata (CEFA). \Ostrich{} (\textit{sans}
CEFA) recently participated in the 2023~SMT-COMP, winning the single-query track
for quantifier-free strings (\texttt{QF\_S}) as well as the entire string
solving track on unsatisfiable instances~\cite{smt-comp-23}.

The \texttt{QF\_S} track contains no Parikh automata intersection problems,
however. For that, we need to look to the linear integer arithmetic
(\texttt{QF\_SLIA}), where \Ostrich{} did worse in SMT-COMP. The evaluations in
\cref{sec:scaling} use inputs generated by an older branch of CEFA-enriched
\Ostrich{} on the PyEx benchmarks, which are part of the set used in the
competition. In this section, we evaluated a version of \Ostrich{} using
\Catra{} as its back-end \Fudge{on StarExec, the same cluster SMT-COMP ran on}
on \numprint{1000}~randomly selected instances from the PyEx benchmarks. The
results are shown in comparison \Fudge{to the other provers of the 2023
competition on the same benchmarks, as well as \Ostrich{} using the baseline
back-end described in \cref{sec:implementing-baseline}}.

\Fudge{RESULTS HERE PLEASE!}
